#Process pupil and behavioral data for Auditory 2AFC task

This script takes processed behavioral, simulation, pupil, and fit data and puts it all into one place so that it can be used in the figure/analysis data frames
```{r}
library(data.table)
library(matrixStats)
library(lme4)
library(tidyr)
library(plyr)
library(lmerTest)
library(parallel)
library(ggplot2)

# Load trial by trial pupil data
pdat = fread('../data/pdat.csv',sep=',')
```

Figure 2b - Influence of switches on baseline pupil diameter
```{r}
getBaseRSwlme = function(dat,h){
  # Function to get beta weights from linear mixed effects model for baseline before tone
  # Convert to data frame and subset hazard rate
  dat2 = data.frame(dat)
  pdat.base = subset(dat2,Hazard == h)
  
  # Scale variables for analysis
  pdat.base$Baseline = scale(pdat.base$Baseline)
  pdat.base$Change_1 = scale(pdat.base$Change_1)
  pdat.base$StimSwitch = scale(pdat.base$StimSwitch)
  pdat.base$RespSwitch = scale(pdat.base$RespSwitch)

  # Run linear mixed effects model
  base.rsw.lme = lmer(Baseline~StimSwitch+RespSwitch+Change_1+
                           (1|Subject)+(1+StimSwitch|Subject)+(1+RespSwitch|Subject)+(1+Change_1|Subject),
                         pdat.base,REML=F,control=lmerControl(calc.derivs=F,optimize='nloptwrap'))
  
  # Save model summary and coefficients
  base.coef = data.frame(coef(base.rsw.lme)$Subject)
  base.coef$Subject = row.names(base.coef)
  base.coef$Hazard = h
  return(list(Summary = summary(base.rsw.lme), Betas = base.coef))
}

# Get beta weights for each hazard rate
h1_base_rsw_lme = getBaseRSwlme(pdat,0.01)
h3_base_rsw_lme = getBaseRSwlme(pdat,0.3)
h9_base_rsw_lme = getBaseRSwlme(pdat,0.99)

# Plot results
h_base_rsw = rbind(h1_base_rsw_lme$Betas,h3_base_rsw_lme$Betas,h9_base_rsw_lme$Betas)
h_base_rsw$Hazard = factor(h_base_rsw$Hazard,levels=c(0.01,.3,.99),labels=c("H = 0.01","H = 0.3", "H = 0.99"))
h_base_rsw.long = gather(h_base_rsw,Type,Beta,StimSwitch:RespSwitch)
h_base_rsw.long$Type = factor(h_base_rsw.long$Type,levels=c("StimSwitch","RespSwitch"),labels=c('Tone Switch','Prediction Switch'))

base_rsw_plt = ggplot(subset(h_base_rsw.long,is.na(Type)==0),aes(Type,Beta,color=Hazard,fill=Hazard,alpha=Type))+
  geom_hline(yintercept=c(0),linetype=3)+
  geom_boxplot()+
  scale_alpha_manual(values=c(0,.7))+
  facet_wrap(~Hazard)+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  ylab("Baseline Beta")+
  ggtitle('Baseline After Tone')+
  ylim(c(-.2,.2))+
    theme(
      legend.position = 'none',
      plot.title = element_text(size=18,face='bold',hjust=.5),
      axis.text.y = element_text(size=12,color='black'),
      axis.text.x = element_text(size=12,color='black',angle=315,vjust=0.5,hjust=0),
      axis.title.y = element_text(size=14,color='black'),
      axis.title.x = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size=16,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
base_rsw_plt
ggsave('./base_rsw.pdf',plot=base_rsw_plt,width = 4,height=5)
```

Figure 2c - Influence of switches on next baseline pupil diameter
```{r}
getBase1RSwlme = function(dat,h){
  # Function to get beta weights from linear mixed effects model for baseline after tone
  # Convert to data frame and subset hazard rate
  dat2 = data.frame(dat)
  pdat.base1 = subset(dat2,Hazard == h)
  
  # Scale variables for analysis
  pdat.base1$Baseline_plus_1 = scale(pdat.base1$Baseline_plus_1)
  pdat.base1$Change = scale(pdat.base1$Change)
  pdat.base1$StimSwitch = scale(pdat.base1$StimSwitch)
  pdat.base1$RespSwitch = scale(pdat.base1$RespSwitch)
  
  # Run linear mixed effects model
  base1.rsw.lme = lmer(Baseline_plus_1~StimSwitch+RespSwitch+Change+
                           (1|Subject)+(1+StimSwitch|Subject)+(1+RespSwitch|Subject)+(1+Change|Subject),
                         pdat.base1,REML=F,control=lmerControl(calc.derivs=F,optimize='nloptwrap'))
  
  # Save model summary and coefficients
  base1.coef = data.frame(coef(base1.rsw.lme)$Subject)
  base1.coef$Subject = row.names(base1.coef)
  base1.coef$Hazard = h
  return(list(Summary = summary(base1.rsw.lme), Betas = base1.coef))
}

# Get beta weights for each hazard rate
h1_base1_rsw_lme = getBase1RSwlme(pdat,0.01)
h3_base1_rsw_lme = getBase1RSwlme(pdat,0.3)
h9_base1_rsw_lme = getBase1RSwlme(pdat,0.99)

# Plot results
h_base1_rsw = rbind(h1_base1_rsw_lme$Betas,h3_base1_rsw_lme$Betas,h9_base1_rsw_lme$Betas)
h_base1_rsw$Hazard = factor(h_base1_rsw$Hazard,levels=c(0.01,.3,.99),labels=c("H = 0.01","H = 0.3", "H = 0.99"))
h_base1_rsw.long = gather(h_base1_rsw,Type,Beta,StimSwitch:RespSwitch)
h_base1_rsw.long$Type = factor(h_base1_rsw.long$Type,levels=c("StimSwitch","RespSwitch"),labels=c('Tone Switch','Prediction Switch'))

base1_rsw_plt = ggplot(subset(h_base1_rsw.long,is.na(Type)==0),aes(Type,Beta,color=Hazard,fill=Hazard,alpha=Type))+
  geom_hline(yintercept=c(0),linetype=3)+
  geom_boxplot()+
  scale_alpha_manual(values=c(0,.7))+
  facet_wrap(~Hazard)+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  ylab("Baseline Beta")+
  ggtitle('Baseline After Tone')+
  ylim(c(-.2,.2))+
    theme(
      legend.position = 'none',
      plot.title = element_text(size=18,face='bold',hjust=.5),
      axis.text.y = element_text(size=12,color='black'),
      axis.text.x = element_text(size=12,color='black',angle=315,vjust=0.5,hjust=0),
      axis.title.y = element_text(size=14,color='black'),
      axis.title.x = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size=16,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
base1_rsw_plt
ggsave('./base1_rsw.pdf',plot=base1_rsw_plt,width = 4,height=5)
```



Compute the beta weights for each sample from tone onset (evoked change = EC)
```{r}
# Function to get beta values for individual sample points from tone onset
getECBeta = function(dat,h){
  # INPUT:
  # dat - pupil data frame with the particular sample you want in index position 8
  # h - hazard rate
  d = subset(dat,Hazard == h)
  names(d)[8] = 'Pupil'
  d$PupilDiff = d$Pupil-d$Baseline
  
  # Scale variables
  d$PupilDiff = scale(d$PupilDiff)
  d$StimSwitch = scale(d$StimSwitch)
  d$RespSwitch = scale(d$RespSwitch)
  d$Baseline = scale(d$Baseline)
  d$Baseline_1 = scale(d$Baseline_1)
  d$Change_1 = scale(d$Change_1)
  
  # Compute linear mixed effects for stimulus switch and non-switch
  ec_lme = lmer(PupilDiff~StimSwitch*RespSwitch+Baseline+Baseline_1+Change_1+
                  (1|Subject)+(1+StimSwitch*RespSwitch|Subject)+(1+Baseline|Subject)+(1+Baseline_1|Subject)+(1+Change_1|Subject),
                d,REML=F,control=lmerControl(calc.derivs=F,optimize='nloptwrap'))
  df = coef(base_lme)$Subject
  df$Subject =row.names(df)
  df$Hazard = h  
  return(list(summary(ec_lme),df))  
}

# Compute LMEs for 120 timepoints after tone onset - takes ~ 6 hours on a quadcore macbook pro
pdat_ec = pdat[,c(2,4,9,11,140,143,145,20:139)]
ncores = 8
cl = makeCluster(ncores)
clusterExport(cl = cl,varlist = c('getECBeta','pdat_ec','lmer','lmerControl','scale'))
h1.sw.rsw.samples = parLapply(cl,1:120,function(x) getECBeta(pdat_ec[pdat_ec$Hazard == 0.01,c(1:7,7+x)]))
saveRDS(base_sw_rsw_h,'./ec_sw_rsw_h1.rds')
h3.sw.rsw.samples = parLapply(cl,1:120,function(x) getECBeta(pdat_ec[pdat_ec$Hazard == 0.3,c(1:7,7+x)]))
saveRDS(base_sw_rsw_h,'./ec_sw_rsw_h3.rds')
h9.sw.rsw.samples = parLapply(cl,1:120,function(x) getECBeta(pdat_ec[pdat_ec$Hazard == 0.99,c(1:7,7+x)]))
saveRDS(base_sw_rsw_h,'./ec_sw_rsw_h9.rds')
stopCluster(cl)
```

Evoked change effects - get p-values
```{r}
#Get significance values for 10 different time points after stim onset
# Not the cleanest....but get everage pupil for 10 equal time points
pdat_ec_rsw = pdat[,c(2,4,9,11,140,143,145,20:139)]
pdat_ec_rsw[,("Hazard"):= factor(pdat_ec_rsw$Hazard,labels=c("H = .01","H = .3","H = .99"))]
pdat_ec_rsw = data.frame(pdat_ec_rsw)
intervals = seq(9,128,120/10)
library(parallel)
cl = makeCluster(8)
clusterExport(cl = cl,varlist = c('pdat_ec_rsw','lapply','intervals'))
pdat_ec_rsw$T1 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[1]:intervals[1]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T2 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[2]:intervals[2]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T3 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[3]:intervals[3]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T4 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[4]:intervals[4]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T5 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[5]:intervals[5]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T6 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[6]:intervals[6]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T7 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[7]:intervals[7]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T8 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[8]:intervals[8]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T9 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[9]:intervals[9]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
pdat_ec_rsw$T10 = parSapply(cl,1:length(pdat_ec_rsw$Sample10), function(x) mean(as.numeric(pdat_ec_rsw[x,intervals[10]:intervals[10]+11])-pdat_ec_rsw$Baseline[x],na.rm=T))
stopCluster(cl)

pdat_ec_rsw_ps = pdat_ec_rsw[,c(1:7,128:137)]
#Get summary for stim and resp switch for each mean timepoint
getPupilSumm = function(dat){
  names(dat)[7] = 'PupilDiff'
  dat$StimSwitch = scale(dat$StimSwitch)
  dat$RespSwitch = scale(dat$RespSwitch)
  dat$PupilDiff = scale(dat$PupilDiff)
  dat$Baseline = scale(dat$Baseline)
  dat$Baseline_1 = scale(dat$Baseline_1)
  dat$Change_1 = scale(dat$Change_1)

  # Linear mixed effects model
  dat.lme = lmer(PupilDiff~RespSwitch*StimSwitch+Baseline+Baseline_1+Change_1+
                     (1|Subject)+(1+RespSwitch*StimSwitch|Subject)+(1+Baseline|Subject)+(1+Baseline_1|Subject)+(1+Change_1|Subject),
                   dat,REML=F,control=lmerControl(calc.derivs=F,optimize='nloptwrap'))   
  return(summary(dat.lme))
}

#Separate 120 samples into 10 different time points
library(parallel)
cl = makeCluster(8)
clusterExport(cl = cl,varlist = c('pdat_ec_rsw_ps','getPupilSumm','lmer','lmerControl','scale'))
h1_rsw_ps = parLapply(cl,1:10,function(x) getPupilSumm(pdat_ec_rsw_ps[pdat_ec_rsw_ps$Hazard == 'H = .01',c(1:7,7+x)],rt=F))
saveRDS(h1_rsw_ps,'./h1_rsw_ps.rds')
h3_rsw_ps = parLapply(cl,1:10,function(x) getPupilSumm(pdat_ec_rsw_ps[pdat_ec_rsw_ps$Hazard == 'H = .3',c(1:7,7+x)],rt=F))
saveRDS(h3_rsw_ps,'./h3_rsw_ps.rds')
h9_rsw_ps = parLapply(cl,1:10,function(x) getPupilSumm(pdat_ec_rsw_ps[pdat_ec_rsw_ps$Hazard == 'H = .99',c(1:7,7+x)],rt=F))
saveRDS(h9_rsw_ps,'./h9_rsw_ps.rds')
stopCluster(cl)
```


```{r}
# Evoked change - load previously computed samples

# Load beta weights for each hazard rate
h1.sw.rsw.samples = readRDS('./ec_sw_rsw_h1.rds')
h3.sw.rsw.samples = readRDS('./ec_sw_rsw_h3.rds')
h9.sw.rsw.samples = readRDS('./ec_sw_rsw_h9.rds')

# Load p-values for 10 time points
h1_rsw_ps = readRDS('./h1_rsw_ps.rds')
h3_rsw_ps = readRDS('./h3_rsw_ps.rds')
h9_rsw_ps = readRDS('./h9_rsw_ps.rds')

# Function to extract previously computed beta weights
getSampleBetas = function(samples,h){
  
  # Ugly...but vectors to extract beta weights
  # Tone switch beta weights (mean and plus/minus standard errors)
  betas.sw = c()
  betas.sw.mse = c()
  betas.sw.pse = c()
  
  # Response switch beta weights (mean and plus/minus standard errors)
  betas.rsw = c()
  betas.rsw.mse = c()
  betas.rsw.pse = c()

  for(i in 1:length(samples[1,])){
    betas = samples[,i][[1]]
    coefs = samples[,i][[2]]
    
    betas.sw[i] = betas$coefficients[2,1]
    betas.sw.mse[i] = mean_se(coefs$StimSwitch)[[2]]
    betas.sw.pse[i] = mean_se(coefs$StimSwitch)[[3]]
    
    betas.rsw[i] = betas$coefficients[3,1]
    betas.rsw.mse[i] = mean_se(coefs$RespSwitch)[[2]]
    betas.rsw.pse[i] = mean_se(coefs$RespSwitch)[[3]]
  }
  return(data.frame(Hazard=rep(h,length(samples[1,])*2),
                    Sample = rep(0:119,2),
                    Factor = c(rep("Stim",length(samples[1,])),rep("Resp",length(samples[1,]))),
                    Betas = c(betas.sw,betas.rsw),
                    mse = c(betas.sw.mse,betas.rsw.mse),
                    pse = c(betas.sw.pse,betas.rsw.pse)))
}

# Function to extract p values in the 10 time points
getBinPval = function(samples,ps){
  samps = unique(samples$Sample)
  #Tone Switch
  stimind = 1
  for(i in 1:length(samps)){
    samples$Ps[samples$Factor == 'Stim' & samples$Sample == samps[i]] = ps[[stimind]]$coefficients[3,5]
    if(i%%12 == 0){
      stimind = stimind + 1
    }
  }
  
  #Resp Switch
  respind = 1
  for(i in 1:length(samps)){
    samples$Ps[samples$Factor == 'Resp' & samples$Sample == samps[i]] = ps[[respind]]$coefficients[2,5]
    if(i%%12 == 0){
      respind = respind + 1
    }
  }
  return(samples)
}

# Use funtions above to extract beta weights and p-values
h1.samples.df = getSampleBetas(h1.sw.rsw.samples,"H = .01")
h3.samples.df = getSampleBetas(h3.sw.rsw.samples,"H = .3")
h9.samples.df = getSampleBetas(h9.sw.rsw.samples,"H = .99")

h1.samples.df = getBinPval(h1.samples.df,h1_rsw_ps)
h3.samples.df = getBinPval(h3.samples.df,h3_rsw_ps)
h9.samples.df = getBinPval(h9.samples.df,h9_rsw_ps)

# Add columns to indicate p-values that reach significance
h.samples.df = rbind(h1.samples.df,h3.samples.df,h9.samples.df)
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .01','H = .3') &h.samples.df$Factor == 'Stim' & h.samples.df$Ps < (.05/10)] = .11
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .01','H = .3') &h.samples.df$Factor == 'Resp' & h.samples.df$Ps < (.05/10)] = .1
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .99') &h.samples.df$Factor == 'Stim' & h.samples.df$Ps < (.05/10)] = -.06
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .99') &h.samples.df$Factor == 'Resp' & h.samples.df$Ps < (.05/10)] = -.07

# Plot
samp.beta.plt = ggplot(h.samples.df,aes(Sample,Betas,alpha=Factor))+
  geom_hline(yintercept=c(0),linetype=3,alpha=.6)+
  geom_ribbon(aes(x=Sample,ymin=mse,ymax=pse,linetype=Factor,color=Hazard,fill=Hazard))+
  geom_line(aes(color=Hazard,linetype=Factor),alpha=1,size=1)+
  geom_line(aes(x = Sample,y=Sig,linetype=Factor,color=Hazard),size=1,alpha=1)+
  facet_wrap(~Hazard)+
  ylab('Evoked Change Beta')+
  xlab('Time from Tone Onset (sec)')+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_alpha_manual(values=c(.6,.3,0))+
  scale_x_continuous(breaks=c(0,60,119),label=c(0,1,2))+
  scale_linetype_manual(values=c(1,2,3))+
  ylim(c(-.07,.11))+
    theme(
      legend.position='none',
      axis.text = element_text(size=12,color='black'),
      axis.title = element_text(size=14,color='black'),
      strip.background = element_blank(),
      strip.text = element_text(size=16,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
samp.beta.plt
ggsave('./ec_rsw.pdf',plot=samp.beta.plt,width = 10,height=5.2)
```

Baseline and next baseline
```{r}
# Get means beta weights and standard errors for each switch type for each hazard rate
halls = list(h1.sw.rsw.all,h3.sw.rsw.all,h9.sw.rsw.all)

# means for baseline before hearing tone
b.means = c()
b.mse = c()
b.pse = c()
b.ts = c()

#means for next baseline
b1.means = c()
b1.mse = c()
b1.pse = c()
b1.ts = c()
ind = 1
for(i in 1:3){
  h.sw.rsw = halls[[i]]
  b.means[ind:(ind+2)] = c(mean(h.sw.rsw[,1][[3]]$StimSwitch),mean(h.sw.rsw[,1][[3]]$RespSwitch),mean(h.sw.rsw[,1][[3]]$StimSwitch.RespSwitch))
  b.mse[ind:(ind+2)] = c(mean_se(h.sw.rsw[,1][[3]]$StimSwitch)[[2]],mean_se(h.sw.rsw[,1][[3]]$RespSwitch)[[2]],mean_se(h.sw.rsw[,1][[3]]$StimSwitch.RespSwitch)[[2]])
  b.pse[ind:(ind+2)] = c(mean_se(h.sw.rsw[,1][[3]]$StimSwitch)[[3]],mean_se(h.sw.rsw[,1][[3]]$RespSwitch)[[3]],mean_se(h.sw.rsw[,1][[3]]$StimSwitch.RespSwitch)[[3]])
  b.ts[ind:(ind+2)] = c(h.sw.rsw[,1][[2]]$coefficients[2,5],h.sw.rsw[,1][[2]]$coefficients[3,5],h.sw.rsw[,1][[2]]$coefficients[6,5])
  
  b1.means[ind:(ind+2)] = c(mean(h.sw.rsw[,4][[3]]$StimSwitch),mean(h.sw.rsw[,4][[3]]$RespSwitch),mean(h.sw.rsw[,4][[3]]$StimSwitch.RespSwitch))
  b1.mse[ind:(ind+2)] = c(mean_se(h.sw.rsw[,4][[3]]$StimSwitch)[[2]],mean_se(h.sw.rsw[,4][[3]]$RespSwitch)[[2]],mean_se(h.sw.rsw[,4][[3]]$StimSwitch.RespSwitch)[[2]])
  b1.pse[ind:(ind+2)] = c(mean_se(h.sw.rsw[,4][[3]]$StimSwitch)[[3]],mean_se(h.sw.rsw[,4][[3]]$RespSwitch)[[3]],mean_se(h.sw.rsw[,4][[3]]$StimSwitch.RespSwitch)[[3]])
  b1.ts[ind:(ind+2)] = c(h.sw.rsw[,4][[2]]$coefficients[2,5],h.sw.rsw[,4][[2]]$coefficients[3,5],h.sw.rsw[,4][[2]]$coefficients[6,5])
  ind = ind+3
}

base.bb = data.frame(Hazard = c(rep('H = .01',3),rep('H = .3',3),rep('H = .99',3)),
                  Factor = rep(c('Stim','Resp','StimxResp'),3),
                  Betas = b.means,
                  MSE = b.mse,
                  PSE = b.pse,
                  Ts = b.ts)

base1.bb = data.frame(Hazard = c(rep('H = .01',3),rep('H = .3',3),rep('H = .99',3)),
                  Factor = rep(c('Stim','Resp','StimxResp'),3),
                  Betas = b1.means,
                  MSE = b1.mse,
                  PSE = b1.pse,
                  Ts = b1.ts)

base.beta.plt = ggplot(subset(base.bb,Factor %in% c('Stim','Resp')),aes(Factor,Betas, alpha=Factor,color=Hazard,fill=Hazard))+
  geom_hline(yintercept=c(0),linetype=3)+
  geom_bar(stat='identity')+
  geom_errorbar(aes(x=Factor,ymin=MSE,ymax=PSE),width=0,size=2,alpha = 1,color='black')+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_alpha_manual(values=c(1,.3))+
  facet_wrap(~Hazard)+
    theme(
      legend.position='none',
      axis.text.y = element_text(size=12,color='black'),
      axis.text.x = element_text(size=12,color='black',angle=315,vjust=0.5,hjust=0),
      axis.title.y = element_text(size=14,color='black'),
      axis.title.x = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size=16,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
ggsave('/Users/alsfilip/Dropbox/Penn/Auditory_2AFC/Auditory_2AFC/Figures/Fig3_pieces/Baseline_Betas.pdf',plot=base.beta.plt,height = 5.2,width = 4.5)

base1.beta.plt=ggplot(subset(base1.bb,Factor %in% c('Stim','Resp')),aes(Factor,Betas,alpha=Factor,color=Hazard,fill=Hazard))+
  geom_hline(yintercept=c(0),linetype=3)+
  geom_bar(stat='identity')+
  geom_errorbar(aes(x=Factor,ymin=MSE,ymax=PSE),width=0,size=2,alpha=1,color='black')+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_alpha_manual(values=c(1,.3))+
  facet_wrap(~Hazard)+
    theme(
      legend.position='none',
      axis.text.y = element_text(size=12,color='black'),
      axis.text.x = element_text(size=12,color='black',angle=315,vjust=0.5,hjust=0),
      axis.title.y = element_text(size=14,color='black'),
      axis.title.x = element_blank(),
      strip.background = element_blank(),
      strip.text = element_text(size=16,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
ggsave('/Users/alsfilip/Dropbox/Penn/Auditory_2AFC/Auditory_2AFC/Figures/Fig3_Pieces/Baseline1_Betas.pdf',plot=base1.beta.plt,height = 5.2,width = 4.5)
```

Evoked change
```{r}
#Plot sample by sample
getSampleBetas = function(samples,h){
  betas.sw = c()
  betas.sw.mse = c()
  betas.sw.pse = c()
  
  betas.rsw = c()
  betas.rsw.mse = c()
  betas.rsw.pse = c()
  
  betas.sw.rsw = c()
  betas.sw.rsw.mse = c()
  betas.sw.rsw.pse = c()
  
  ts.sw = c()
  ts.rsw = c()
  ts.sw.rsw = c()
  for(i in 1:length(samples[1,])){
    betas = samples[,i][[1]]
    coefs = samples[,i][[2]]
    
    betas.sw[i] = betas$coefficients[2,1]
    betas.sw.mse[i] = mean_se(coefs$StimSwitch)[[2]]
    betas.sw.pse[i] = mean_se(coefs$StimSwitch)[[3]]
    
    betas.rsw[i] = betas$coefficients[3,1]
    betas.rsw.mse[i] = mean_se(coefs$RespSwitch)[[2]]
    betas.rsw.pse[i] = mean_se(coefs$RespSwitch)[[3]]
    
    betas.sw.rsw[i] = betas$coefficients[7,1]
    betas.sw.rsw.mse[i] = mean_se(coefs$StimSwitch.RespSwitch)[[2]]
    betas.sw.rsw.pse[i] = mean_se(coefs$StimSwitch.RespSwitch)[[3]]
    
    ts.sw[i] = betas$coefficients[2,5]
    ts.rsw[i] = betas$coefficients[3,5]
    ts.sw.rsw[i] = betas$coefficients[7,5]
  }
  return(data.frame(Hazard=rep(h,length(samples[1,])*3),
                    Sample = rep(0:119,3),
                    Factor = c(rep("Stim",length(samples[1,])),rep("Resp",length(samples[1,])),rep("StimxResp",length(samples[1,]))),
                    Betas = c(betas.sw,betas.rsw,betas.sw.rsw),
                    mse = c(betas.sw.mse,betas.rsw.mse,betas.sw.rsw.mse),
                    pse = c(betas.sw.pse,betas.rsw.pse,betas.sw.rsw.pse),
                    Ts = c(ts.sw,ts.rsw,ts.sw.rsw)))
  }

h1.samples.df = getSampleBetas(h1.sw.rsw.samples,"H = .01")
h3.samples.df = getSampleBetas(h3.sw.rsw.samples,"H = .3")
h9.samples.df = getSampleBetas(h9.sw.rsw.samples,"H = .99")

h.samples.df = rbind(h1.samples.df,h3.samples.df,h9.samples.df)
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .01','H = .3') &h.samples.df$Factor == 'Stim' & h.samples.df$Ts < (.05/10)] = .11
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .01','H = .3') &h.samples.df$Factor == 'Resp' & h.samples.df$Ts < (.05/10)] = .1
h.samples.df$Sig[h.samples.df$Factor == 'StimxResp' & h.samples.df$Ts < (1/120)] = -.09
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .99') &h.samples.df$Factor == 'Stim' & h.samples.df$Ts < (.05/10)] = -.07
h.samples.df$Sig[h.samples.df$Hazard %in% c('H = .99') &h.samples.df$Factor == 'Resp' & h.samples.df$Ts < (.05/10)] = -.06


samp.beta.plt = ggplot(subset(h.samples.df,Factor %in% c('Stim','Resp')),aes(Sample,Betas,alpha=Factor))+
  geom_hline(yintercept=c(0),linetype=2,size=1,alpha=.6)+
  geom_ribbon(aes(x=Sample,ymin=mse,ymax=pse,linetype=Factor,color=Hazard,fill=Hazard))+
  geom_line(aes(color=Hazard,linetype=Factor),alpha=1,size=1)+
  geom_line(aes(x = Sample,y=Sig,linetype=Factor,color=Hazard),size=1,alpha=1)+
  facet_wrap(~Hazard)+
  ylab('Beta Weight')+
  xlab('Time from Tone Onset (sec)')+
  scale_color_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_fill_manual(values=c("#0072B2","#D55E00","#E69F00"))+
  scale_alpha_manual(values=c(.6,.3,0))+
  scale_x_continuous(breaks=c(0,60,119),label=c(0,1,2))+
  scale_linetype_manual(values=c(1,2,3))+
  ylim(c(-.07,.11))+
    theme(
      axis.text = element_text(size=12,color='black'),
      axis.title = element_text(size=14,color='black'),
      strip.background = element_blank(),
      strip.text = element_text(size=12,color='black',face='bold'),
      axis.line.x = element_line(size = .5,color="black"),
      axis.line.y = element_line(size=.5,color="black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
    )
ggsave(paste0(root,'Figures/Fig3_pieces/Samples_Betas.pdf'),plot=samp.beta.plt,width = 9,height=4)
```

